A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2018-03-12 analysis/paper/paper.Rmd
get osfr from github, and larger data files from osf, since they wont fit on GH

# Download from osf.io with this:
# library(osfr)
# download_file("tsm89", private = TRUE)

dc_arch <- readRDS("../data/raw_data/dc_arch.rds")
dc_arch_tdar <- readRDS("../data/raw_data/dc_arch_tdar.rds")
dc_arch <- bind_rows(dc_arch, dc_arch_tdar)
```

>>>>

# Download from osf.io with this:

# devtools::install_github("chartgerink/osfr")
# library(osfr)
# download_files("tsm89", path = '../data/raw_data/')
# download_files("z9w6j", path = '../data/raw_data/')

if(!file.exists("../data/raw_data/dc_arch.rds")){
    osfr::download_files("tsm89", path = '../data/raw_data/')
 }
dc_arch <- readRDS("../data/raw_data/dc_arch.rds")

if(!file.exists("../data/raw_data/dc_arch_tdar.rds")){
    osfr::download_files("z9w6j", path = '../data/raw_data/')
 }
dc_arch_tdar <- readRDS("../data/raw_data/dc_arch_tdar.rds")

dc_arch <- bind_rows(dc_arch, dc_arch_tdar)
```
